---
title: "Homework 02"
editor: 
  markdown: 
    wrap: 72
---

## TidyTuesday Part (Optional)

::: {.callout-important title="Instructions"}
You can count work on this week's TidyTuesday toward the exceptional
work.
:::

Explore the week's
[TidyTuesday](https://github.com/rfordatascience/tidytuesday) challenge.
Develop a research question, then answer it through a short data story
mainly composed of [effective
visualizations](https://docs.google.com/presentation/d/1WHr6Itzm2IJLxvppcacxHpr8R4NxO4MfvWWUPmtQx6Q/preview?slide=id.g13360dab5d5_0_61).
Provide sufficient background for readers to grasp your narrative. Refer
to the Homework Instructions ⭐ page on the course website for details
on how to submit this part.

```{r}
dead_scrolls<-read.csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-09-15/dead_sea_scrolls.csv')
```

**Background** The dead_scrolls dataset was curated by Tony Galvan of
Golden Dome Data Science using information from the Israel Antiquities
Authority's official Leon Levy Dead Sea Scrolls Digital Library. The
dataset contains information about the Dead Sea Scrolls discovered near
the Dead Sea. It includes variables such as the manuscript ID, the cave
where the manuscript was found, the material it was made from, the
discovery site, and the parent site.

I will use these variables to explore the types of texts found at
different sites and consider what these texts may suggest about the
beliefs and practices of the communities associated with those
locations.

```{r}
#library(tidyverse)
#dead_scrolls|>
#  ggplot(aes(y=num_images,x=site_parent,colour  = biblical_book))+
 # geom_point()+
  #labs(title = "A graph of the number of images",subtitle = "Number of high resolution images for the manuscript")
  
```

```{r}
dead_scrolls|>
  filter(composition!="Unidentified")|>
  group_by(composition)|>
  ggplot(aes(x=composition))+
  geom_bar()+
  labs(title = "composition or biblical book identified ")
```

```{r}
dead_scrolls|>
filter(composition!="Unidentified")|>
  group_by(site)



```

```{r}
dead_scrolls|>
  ggplot(aes(x=language))+
  geom_bar()+
  labs(title = "language of manuscript ")
```

```{r}
dead_scrolls|>
  group_by(site_parent)|>
  ggplot(aes(x=site))+
  geom_boxplot()+
  labs(title = "full discovery site description ")

```

```{r}
dead_scrolls|>
  ggplot(aes(x=biblical_book))+
  geom_bar()+
  labs(title = "Identified Biblical book")
```

```{r}
dead_scrolls|>
  filter(!bible_section=="Unidentified")|>
  ggplot(aes(x=bible_section))+
  geom_bar()+
  labs(title = "bible section")
```

**question** What can the distribution of manuscripts found at different
sites tell us about the types of texts associated with the beliefs of
the commnunites around there?

```{r}
dead_scrolls |>
  filter(content_category != "Unidentified") |>
  ggplot(aes(x = site_parent, fill = content_category)) +
  geom_bar() +
  geom_text(stat = "count",
    aes(label = after_stat(count)),
    position = position_stack(vjust = 0.5))+
  labs(
    title = "Types of Texts Found Across Dead Sea Scrolls Sites",
    subtitle = "The Scarcity of Biblical Texts Suggests Broader Religious Traditions",
    x = "Discovery Site",
    y = "Number of Manuscripts",
    fill = "Content Category",
    caption = "Source: Week 2 TidyTuesday, Created on:09/20/26 by :Apiu Kur",
    alt = "A bar chart showing the number of manuscripts in different content categories at each Dead Sea Scrolls discovery site. The x-axis shows discovery sites and the y-axis shows the number of manuscripts. Different colors represent content categories."
  )
```

```{r}
dead_scrolls|>
  ggplot(aes(x=num_images,y=site_parent,colour = content_category))+
  geom_point()+
  facet_wrap(~testament)
```

_The Quamran communities contains the highest number of images taken to
locate the specific manuscript _Qumran has a variety of the category of
the books associated to them varying from Biblical,documentary,wisdom.
-Masada had the wisdom literature. -Wadi Murabbat had a mix of
biblical,Parabiblical -Nahal Hever had Biblical Liturgical -Masada
mostly Biblical.

```{r}
dead_scrolls|>
  ggplot(aes(x=num_images,y=site_parent,colour = testament))+
  geom_point()
```

#observations
Qumran has a large number of manuscripts and contains a
wide variety of text types. Many of the manuscripts found at Qumran are
non-biblical, but the site also contains manuscripts of Old Testament
texts. Masada also contains mostly non-biblical manuscripts. Across the
sites, non-biblical texts make up a large part of the manuscripts,
although the types of texts vary between locations.

The manuscripts found at different Dead Sea Scrolls sites provide clues
about the kinds of texts that were important to the communities
associated with those locations. Qumran stands out because it contains a
large and diverse collection of manuscripts, including both biblical and
non-biblical texts. The presence of Old Testament texts alongside other
types of writings suggests that the community engaged with biblical
traditions while also reading and producing other kinds of texts.

The large number of non-biblical manuscripts could mean that the
communities had a broader range of beliefs, practices, laws, wisdom, and
other ideas that were important to the communities.
